---
title: "Lanes Island Living Shorelines Elevations, 2021"
author: "Curtis C. Bohlen"
date: '2022-06-28'
output: slidy_presentation 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE,
                      fig.align = 'center',
                      collapse = TRUE, comment = "#>")
```

# Libraries Used
```{r include = TRUE, echo = TRUE, message = FALSE}
library(tidyverse)
library(readr)
library(plotly)
```


```{r}
theme_set(theme_minimal())
```

``

# Generating Static Output
The `save_image()` function has external dependencies on the `kaleido` python
package, the `plotly` **python** package and on the `reticulate` R package.  I
had to figure out which python installation R was calling, and then install
`kaleido` and `plotly` via conda in the relevant anaconda environment.


# Load Data
First, we read in data related to setting up the Total Station.
```{r include = TRUE, echo = TRUE, warning = TRUE}
the_data_setup<- read_csv("2021.TXT", col_names = FALSE, 
                          col_types = "idddcc", n_max = 6)
```

The `read_csv()` function determines the number of data columns based on the
first few rows of data. I could not find a way to get it to recognize the sixth
```{r  include = TRUE, echo = TRUE}
problems(the_data_setup)
```

Then we read in the rest of the data. Unfortunately, the number of rows to skip 
is file-specific, so probably needs to be based on visual inspection of each 
file.

```{r include = TRUE, echo = TRUE}
the_data <- read_csv("2021.TXT", skip = 7,
                     col_names = FALSE, 
                     col_types = "idddccccccc")

names(the_data ) <- c("Index", "Easting", "Northing", "Elevation", "Name", 
                      "Date", "Time", "Inst_Hgt", "Rod_Hgt", "PRSMBS", "PRSMFS")

the_data <- the_data %>%
  mutate(Date = sub("DATE:", "", Date),
         Time = sub("TIME:", "", Time),
         Inst_Hgt  = as.numeric(sub("INSTHGT:", "", Inst_Hgt)),
         Rod_Hgt  = as.numeric(sub("RODHGT:", "", Inst_Hgt)),
         PRSMBS  = as.numeric(sub("PRSMBS:", "", PRSMBS)),
         PRSMFS  = as.numeric(sub("PRSMFS:", "", PRSMFS))
         ) %>%
  mutate(Date = as.Date(Date, format = '%m-%d-%Y'),
         Time = strptime(Time, format = '%H:%M:%S', tz = "America/New_York"))
```

#  More Data Manipulation
We need to create some different data columns to simplify plotting.

```{r include = TRUE, echo = TRUE}
the_data <- the_data %>%
  mutate(group = if_else(grepl('CROSS', Name), 'Cross Sections',
                         if_else(grepl('SCARP', Name), "Scarp",
                                 if_else(grepl('LOG', Name), 'Structure', 
                                         'Other')))) %>%
  mutate(group = if_else(group == 'Scarp' & Elevation < 3, "Toe", group)) %>%
  mutate(ShortName = Name,
         ShortName = sub('LOG', '', ShortName),
         ShortName = sub("CROSS#", '', ShortName),
         x = Easting - 4849200,
         y = Northing - 409000

)
```


# First Effort at Plotly
```{r include = TRUE, warning = TRUE}
fig <- the_data %>%
  filter(group == 'Cross Sections') %>%
  group_by(ShortName) %>%
  plot_ly(x = ~x, y = ~y, z = ~Elevation,  color=~Elevation,
                 type = 'scatter3d', mode = 'markers',
          marker = list(size = 5)) %>%
  add_paths(x = ~x, y = ~y, z = ~Elevation, color = ~Elevation,
            showlegend = FALSE, mode = 'paths')
fig
```
```{r fig_1, include = TRUE}
fig <- fig %>%
   layout(scene = list(camera = list(eye = list(x=-1, y =2, z =0.5)),
          aspectmode='data'))
fig
```


# Add The Structure (Logs)
```{r fig_2, include = TRUE}
tmp <- the_data %>% 
  filter(group == 'Structure') %>%
  mutate(grp = substr(ShortName, 1,1)) %>%
  group_by(grp)

fig_2  <- fig %>%
  add_paths(x = ~x, y = ~y, z = ~Elevation, color = I('Gray15'),
          line = list(width = 6), data = tmp,
          showlegend = FALSE)
  
fig_2
```


# Add The Scarp Lines
```{r fig_3, include = TRUE}
top <- the_data %>% 
  filter(group == 'Scarp')
bottom <- the_data %>% 
  filter(group == 'Toe')

fig_3  <- fig_2 %>%
  add_markers(x = ~x, y = ~y, z = ~Elevation, color = I('Gray50'), data = top,
              marker = list(size = 5),
              showlegend = FALSE ) %>%
  add_paths(x = ~x, y = ~y, z = ~Elevation, color = I('Gray50'), data = top ,
            showlegend = FALSE) %>%
    add_markers(x = ~x, y = ~y, z = ~Elevation, color = I('blue'), data = bottom,
              marker = list(size = 5),
              showlegend = FALSE ) %>%
  add_paths(x = ~x, y = ~y, z = ~Elevation, color = I('blue'), data = bottom ,
            showlegend = FALSE)
  
fig_3
```

```{r include = TRUE, echo = TRUE}
save_image(fig_3, file = 'test.png')
```

